---
title: "Crossmodal - instruction file"
author: "Laura Bock Paulsen"
date: "9/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

```{r}
pacman::p_load(tidyverse, readbulk, patchwork, lmerTest)
```

For this class, the aim is to investigate some cross modal effects. This will be done using the data from the experiment you **hopefully** completed before today's class.

There are 4 steps to today's exercise: 

1) Load in data
2) Investigation and preparation of the data
3) Investigate if congruency predicts reaction time using linear regression
4) Visualization of accuracy rate


Enjoy!

## Load in data

### Download data
First of all, you need to download the data from the Google drive folder: **https://drive.google.com/drive/folders/19HsBvrrnRynsn0z90iZhqL5SRaj-nnlw?usp=sharing** or just skip to the next step if you cloned the GitHub repo (data should be included).

### Load data
Load in the data.
```{r}
setwd(".")
df_aud <- read_bulk(directory = "C:/Users/Emili/Documents/University/3rd semester/Perception and Action/PercAct2022/crossmodal/data_aud")
df_vis <- read_bulk(directory = "C:/Users/Emili/Documents/University/3rd semester/Perception and Action/PercAct2022/crossmodal/data_vis")
```

Hint: you can use read_bulk() from the readbulk package to load the different csv files into one dataframe (one df for vision, one for audition). 

```{r}
#viewing the data
view(df_aud)
view(df_vis)
```


### Discussion
Before you start looking at the data, discuss what predictions you have and why. 


# Investigation and preperation of the data

### Data structure
To begin with try to get an overview of the data by answering the following questions:

What variables do we have? 
```{r}
#Getting the variables from each dataframe
ls(df_aud)
ls(df_vis)
```

Which variables are we interested in? 

Are the variables in the right format (e.g., factor, numeric)? If they are not, make sure they are.
```{r}
str(df_aud)
str(df_vis)

#Mutating
# AUDITION 
df_aud <- df_aud %>% 
  mutate(
    accuracy = as.factor(accuracy),
    congruency = as.factor(congruency),
    subject = as.factor(subject)
)

# VISION
df_vis <- df_vis %>% 
  mutate(
    accuracy = as.factor(accuracy),
    congruency = as.factor(congruency),
    subject = as.factor(subject)
)
```

How many participants do we have in each condition?
```{r}
#Participants in vis
length(unique(df_vis$subject))

#Participants in aud
length(unique(df_aud$subject))
```

Create new dataframes that only contains the correct trials. The dataframes with both correct and incorrect trials will be used in the last part of the exercise, so do not overwrite this. 
```{r}
df_aud_new <- df_aud %>% 
  filter(accuracy == "true")
  
df_vis_new <- df_vis %>% 
  filter(accuracy == "true")
```


### Initial plot
To further look into the data, lets make a quick plot! More specifically, make a plot of the mean reaction time per concurrency. Make sure to include errorbars. 

```{r}
# AUDITION
df_aud_new %>% 
  ggplot() +
  aes(x = congruency, y = rt, color = congruency) +
  stat_summary(fun = "mean", geom = "point", size = 3) + #adds mean points
  stat_summary(fun = 'mean', geom = 'line', color = 'gray55', aes(group = 1)) + #adds mean line
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .1) + #adds the mean standard errorbars
  theme(legend.position = 'None') +
  labs(title = 'Mean RT of audition with SE errorbars') +
  theme_classic()

# VISION
df_vis_new %>% 
  ggplot() +
  aes(x = congruency, y = rt, color = congruency) +
  stat_summary(fun = "mean", geom = "point", size = 3) + #adds mean points
  stat_summary(fun = 'mean', geom = 'line', color = 'gray55', aes(group = 1)) + #adds mean line
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .1) + #adds the mean standard errorbars
  theme(legend.position = 'None') +
  labs(title = 'Mean RT of vision with SE errorbars')+
  theme_classic()
```

### Discussion
Interpret the findings. Do they match your predictions? Why? Why not? 


# Investigate if congruency predicts reaction time using a linear model
Does congruency predict the reaction time? Lets find out. 

To do this, make a simple linear model. 
```{r}
model1 <- lmer(rt~congruency + (1|subject), data = df_aud_new)
summary(model1)
```

### Report the results
Imagine this was your exam project. What would you write in the results section? Write a sentence or two reporting the results of the two linear models (APA style).


# Visuallisation of accuracy rate
Make a graph of the accuracy rate. Is there a way to visualize the relationship between congruency and the percentage of incorrectly answered trials per subject?
```{r}

```

Hint: Which data frames contain both correct and incorrect trials?

### Discussion
Discuss the resulting plots. 


## Optional (If you are done before time is up)
Earlier you created a simple linear model to test if congruency predicted the reaction time. Are there other **Cough chough** bayesian **Cough cough** ways to investigate this? If so, give it a go!


